%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
\usepackage[sfdefault]{roboto}  % or FiraSans
\renewcommand{\familydefault}{\sfdefault}

% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Compact version only for certifications
\newcommand{\certItemListStart}{
  \begin{itemize}[leftmargin=*, label=\textbullet, itemsep=2pt, topsep=2pt, parsep=0pt, partopsep=0pt]
}


\newcommand{\certItemListEnd}{\end{itemize}\vspace{-5pt}}
\newcommand{\certItem}[1]{\item\small{#1}\vspace{-2pt}}



\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Soham Das} \\ \vspace{1pt}
    \small Mobile: +91-7980290675 $|$ \href{jisusoham04@gmail.com}{\underline{jisusoham04@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/sohamdas00/}{\underline{linkedin}} $|$
    \href{https://github.com/SohamDas00}{\underline{github}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Dr. Sudhir Chandra Sur Institute of Technology}{Kolkata, India}
      {Bachelor of Technology in Computer Science and Engineering}{2023 -- 2027}
    \resumeSubheading
      {Sudhir Memorial Institute}{Kolkata, India}
      {Higher Secondary, Science Stream CBSE}{2021 - 2023}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Frontend Developer Intern}{Jan 2025 – Apr 2025}
      {Zeptik}{Lucknow}
      \resumeItemListStart
        \resumeItem{Developed 10+ responsive UI pages using React.js and Tailwind CSS, improving cross-device performance.}
        \resumeItem{ Implemented Git branching strategy and reusable component structure for scalable development.}
        \resumeItem{Designed user-centric UI/UX in Figma, improving navigation flow and visual consistency.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Open Source Contributor}{Oct 2024 - Nov 2024}
      {GirlScript Summer of Code}{Remote, India}
      \resumeItemListStart
        \resumeItem{Contributed to 5+ open-source repositories, implementing features and resolving issues via GitHub pull requests.}
        \resumeItem{Collaborated with developers to enhance project features and functionality.}
        \resumeItem{Resolved bugs and implemented enhancements through pull requests, improving code quality and user experience.}
    \resumeItemListEnd

    \resumeSubheading
      {Open Source Contributor}{Oct 2024 - Nov 2024}
      {Hacktoberfest 2024}{Remote, India}
      \resumeItemListStart
        \resumeItem{Contributed to multiple open-source repositories during Hacktoberfest 2024, focusing on collaboration, issue resolution, and documentation enhancements}
        \resumeItem{Promoted innovation and open-source development in collaboration with global tech community.}
        \resumeItem{Improved Git/GitHub proficiency by actively collaborating with developers in distributed teams.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeProjectHeading
        {\textbf{\underline{\href{https://sohamdas-tomato.netlify.app/}{Tomato Food App}}} $|$ \emph{React 18, CSS, Vite, Git} \quad \underline{\href{https://github.com/SohamDas00/tomato-ecommerce-app}{GitHub}}}{April 2025 – May 2025}
        \resumeItemListStart
          \resumeItem{Developed Tomato, a responsive food ordering web app with category filtering, cart management, and checkout flow.}
          \resumeItem{Designed a clean UI with Sign Up/Login (frontend-only) for a complete and intuitive user experience.}
          \resumeItem{Strengthened React skills including useState, useContext, component structuring, and dynamic cart logic.}
          \resumeItem{Deployed the application on Netlify for seamless access and sharing.}
        \resumeItemListEnd

    \resumeProjectHeading
        {\textbf{\underline{\href{https://sohamdas-meme-generator.netlify.app/}{Meme Generator}}} $|$ \emph{React 19, CSS, Git} \quad \underline{\href{https://github.com/SohamDas00/Meme-Generator}{GitHub}}}{Feb 2025 – Mar 2025}
        \resumeItemListStart
          \resumeItem{Built an interactive Meme Generator app that fetches random images via API and overlays custom top/bottom text.}
          \resumeItem{Enabled real-time meme preview and one-click download functionality for user-created memes.}
          \resumeItem{Improved skills in API integration, image manipulation, and React state management.}
          \resumeItem{Deployed the application on Netlify for seamless access and sharing.}
        \resumeItemListEnd
  \resumeSubHeadingListEnd







%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: C++, Python, JavaScript, HTML/CSS} \\
     \textbf{Frameworks}{: React, Tailwind CSS} \\
     \textbf{Operating Systems}{: Windows, Linux} \\
     \textbf{Version Control}{: Git, GitHub} \\
    }}
 \end{itemize}


%-------------------------------------------



%-----------Certifications-----------
\section{Certifications}
\certItemListStart
  \certItem{AI NCAT – Naukri.com}
  \certItem{Namaste JavaScript – NamasteDev.com}
  \certItem{Open Source Contribution – GSSoC, Rank-171}
  \certItem{Postman API Student Expert – Postman}
\certItemListEnd



%-------------------------------------------
\end{document}
